Accuracy and precision of zero-heat-flux temperature measurements with the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System

### 2020-05-06 manuscript/manuscript.Rmd
officedown

```{r global_options, include=FALSE}
knitr::opts_chunk$set(include=TRUE,
                      echo=FALSE, warning=FALSE, message=FALSE)
library(dplyr)
library(ggprisma) # https://github.com/awconway/ggprisma
library(kableExtra)
library(knitr)
library(magrittr)
source(here::here("manuscript", "loa_maker.R"))
source(here::here("manuscript","meta.R"))
library(gofer) # https://github.com/awconway/gofer
library(flextable)
```

>>>>

```{r global_options, include=FALSE}
knitr::opts_chunk$set(include=TRUE,
                      echo=FALSE, warning=FALSE, message=FALSE)
library(dplyr)
library(ggprisma) # https://github.com/awconway/ggprisma
library(knitr)
library(magrittr)
source(here::here("manuscript", "loa_maker.R"))
source(here::here("manuscript","meta.R"))
library(gofer) # https://github.com/awconway/gofer
library(flextable)
```
